Efficient simulation of individual-based population models

### 2024-03-27 article.qmd
digits

print(paste("Execution time : ", sim_out$logs[["duration_ns"]]/1e9, "s", sep=""))

print(paste("Proportion of effective events and proposed events : ", sim_out$logs[["effective_events"]] / sim_out$logs[["proposed_events"]], sep=""))

>>>>

print(paste("Execution time : ", format(sim_out$logs[["duration_ns"]]/1e9,digits = 2), "s", sep=""))

print(paste("Proportion of effective events and proposed events : ", format(sim_out$logs[["effective_events"]] / sim_out$logs[["proposed_events"]], digits=2), sep=""))
